Paper # 1 - Figures

### 2020-03-24 papers/paper-1/paper_1_figures.Rmd
cleaning up

```{r}
# Median
median_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "med_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

@@

# Mean
mean_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

@@

# Weighted Mean
w_mean_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "w_mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

@@

subsidy_intensity_tot_grid_map
ggsave(paste0(results_dir, "subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 12.5)

@@

```{r}
# Median
median_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "med_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

# Mean
mean_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

# Weighted Mean
w_mean_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "w_mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

subsidy_intensity_tot_region_map
ggsave(paste0(results_dir, "subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 12.5)

@@

@@

```{r}
# Median
median_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "med_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

@@

# Mean
mean_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

@@

# Weighted Mean
w_mean_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "w_mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

@@

subsidy_intensity_B_grid_map
ggsave(paste0(results_dir, "subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 12.5)

@@

```{r}
# Median
median_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "med_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

# Mean
mean_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

# Weighted Mean
w_mean_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "w_mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

subsidy_intensity_B_region_map
ggsave(paste0(results_dir, "subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 12.5)

@@

@@

```{r}
# Median
median_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "med_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

@@

# Mean
mean_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

@@

# Weighted Mean
w_mean_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "w_mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land)

@@

subsidy_intensity_BC_grid_map
ggsave(paste0(results_dir, "subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 12.5)

@@

```{r}
# Median
median_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "med_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

# Mean
mean_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

# Weighted Mean
w_mean_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "w_mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

subsidy_intensity_BC_region_map
ggsave(paste0(results_dir, "subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 12.5)

@@

@@

```{r}
# Median
median_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
                                     res = "region",
                                     fill = "med_f_v_fmsy",
                                     fill_name = "F/Fmsy",
                                     fill_breaks = seq(0,4, by = 1),
                                     fill_limits = c(0,4),
                                     fill_labels = c("0", "1", "2", "3", "4"),
                                     land_sf = world_land,
                                     region_sf = fao_regions)

@@

# Mean
mean_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
                                     res = "region",
                                     fill = "mean_f_v_fmsy",
                                     fill_name = "F/Fmsy",
                                     fill_breaks = seq(0,4, by = 1),
                                     fill_limits = c(0,4),
                                     fill_labels = c("0", "1", "2", "3", "4"),
                                     land_sf = world_land,
                                     region_sf = fao_regions)

@@

# Weighted Mean
w_mean_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
                                     res = "region",
                                     fill = "w_mean_f_v_fmsy",
                                     fill_name = "F/Fmsy",
                                     fill_breaks = seq(0,4, by = 1),
                                     fill_limits = c(0,4),
                                     fill_labels = c("0", "1", "2", "3", "4"),
                                     land_sf = world_land,
                                     region_sf = fao_regions)

@@

@@

```{r}
subsidy_intensity_upsides_region <- upsides_region %>%
  left_join(subsidy_intensity_region, by = "fao_region")

# Weighted mean of Bad + Ambig vs Weighted mean F/Fmsy
w_mean_BC_vs_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
                                       res = "corr",
                                       x = "w_mean_BC_subs_KWh",
                                       x_name = "Weighted Mean Subsidy Intensity ($/KWh)",
                                       x_limits = c(0,2),
                                       y = "w_mean_f_v_fmsy",
                                       y_name = "Weighted Mean F/Fmsy",
                                       y_limits = c(0,2.5),
                                       fill = "tot_fishing_KWh",
                                       fill_name = "Total Fishing Effort \n(KWh, billions)",
                                       fill_limits = c(0,7.5e9),
                                       fill_breaks = seq(0,7.5e9, length.out = 5),
                                       fill_labels = format(seq(0,7.5e9, length.out = 5)/1e9, scientific = F, digits = 2))

ggsave(paste0(results_dir, "w_mean_BC_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 7)

# mean of Bad + Ambig vs mean F/Fmsy
w_mean_BC_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
                                       res = "corr",
                                       x = "w_mean_BC_subs_KWh",
                                       x_name = "Weighted Mean Subsidy Intensity ($/KWh)",
                                       x_limits = c(0,4),
                                       y = "med_f_v_fmsy",
                                       y_name = "Median F/Fmsy",
                                       y_limits = c(0,4),
                                       fill = "tot_fishing_KWh",
                                       fill_name = "Total Fishing Effort \n(KWh, billions)",
                                       fill_limits = c(0,7.5e9),
                                       fill_breaks = seq(0,7.5e9, length.out = 5),
                                       fill_labels = format(seq(0,7.5e9, length.out = 5)/1e9, scientific = F, digits = 2))

ggsave(paste0(results_dir, "w_mean_BC_vs_median_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 7)

>>>>

```{r}
# Median
median_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "med_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "\u2265 8"),
                                                  land_sf = world_land)

@@

# Mean
mean_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "\u2265 8"),
                                                  land_sf = world_land)

@@

# Weighted Mean
w_mean_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "w_mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "\u2265 8"),
                                                  land_sf = world_land)

@@

ggsave(paste0(results_dir, "subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 12.5)

@@

```{r}
# Median
median_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "med_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "\u2265 8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

# Mean
mean_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "\u2265 8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

# Weighted Mean
w_mean_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "w_mean_tot_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,8, by = 2),
                                                  fill_limits = c(0,8),
                                                  fill_labels = c("0", "2", "4", "6", "\u2265 8"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

ggsave(paste0(results_dir, "subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 12.5)

@@

```{r, fig.width=14, fig.height=12.5}
# Combine into six panel
subsidy_intensity_tot_noleg <- plot_grid(median_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
                                         median_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
                                         mean_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
                                         mean_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
                                         w_mean_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
                                         w_mean_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
                                         ncol = 2,
                                         labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean", ""),
                                         label_x = c(-0.04, 0, -0.03,0, -0.1, 0))

subsidy_intensity_tot_map <- plot_grid(subsidy_intensity_tot_noleg,
                                       intensity_tot_region_legend,
                                       rel_heights = c(2,0.2),
                                       ncol = 1)

subsidy_intensity_tot_map
ggsave(paste0(results_dir, "subsidy_intensity_tot_map.png"), dpi = 200, width = 14, height = 12.5)
```

@@

```{r}
# Median
median_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "med_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,6, by = 2),
                                                  fill_limits = c(0,6),
                                                  fill_labels = c("0", "2", "4", "\u2265 6"),
                                                  land_sf = world_land)

@@

# Mean
mean_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,6, by = 2),
                                                  fill_limits = c(0,6),
                                                  fill_labels = c("0", "2", "4", "\u2265 6"),
                                                  land_sf = world_land)

@@

# Weighted Mean
w_mean_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "w_mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,6, by = 2),
                                                  fill_limits = c(0,6),
                                                  fill_labels = c("0", "2", "4", "\u2265 6"),
                                                  land_sf = world_land)

@@

ggsave(paste0(results_dir, "subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 12.5)

@@

```{r}
# Median
median_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "med_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,6, by = 2),
                                                  fill_limits = c(0,6),
                                                  fill_labels = c("0", "2", "4", "\u2265 >6"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

# Mean
mean_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,6, by = 2),
                                                  fill_limits = c(0,6),
                                                  fill_labels = c("0", "2", "4", "\u2265 6"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

# Weighted Mean
w_mean_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "w_mean_B_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,6, by = 2),
                                                  fill_limits = c(0,6),
                                                  fill_labels = c("0", "2", "4", "\u2265 6"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

ggsave(paste0(results_dir, "subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 12.5)

@@

```{r, fig.width=14, fig.height=12.5}
# Combine into six panel
subsidy_intensity_B_noleg <- plot_grid(median_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
                                       median_subsidy_intensity_B_region_map + theme(legend.position = "none"),
                                       mean_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
                                       mean_subsidy_intensity_B_region_map + theme(legend.position = "none"),
                                       w_mean_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
                                       w_mean_subsidy_intensity_B_region_map + theme(legend.position = "none"),
                                       ncol = 2,
                                       labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean", ""),
                                       label_x = c(-0.04, 0, -0.03,0, -0.1, 0))

subsidy_intensity_B_map <- plot_grid(subsidy_intensity_B_noleg,
                                       intensity_B_region_legend,
                                       rel_heights = c(2,0.2),
                                       ncol = 1)

subsidy_intensity_B_map

ggsave(paste0(results_dir, "subsidy_intensity_B_map.png"), dpi = 200, width = 14, height = 12.5)
```

@@

```{r}
# Median
median_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "med_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,6, by = 2),
                                                  fill_limits = c(0,6),
                                                  fill_labels = c("0", "2", "4", "\u2265 6"),
                                                  land_sf = world_land)

@@

# Mean
mean_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,6, by = 2),
                                                  fill_limits = c(0,6),
                                                  fill_labels = c("0", "2", "4", "\u2265 6"),
                                                  land_sf = world_land)

@@

# Weighted Mean
w_mean_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
                                                  res = "grid",
                                                  x = "lon_bin_center",
                                                  y = "lat_bin_center",
                                                  fill = "w_mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,6, by = 2),
                                                  fill_limits = c(0,6),
                                                  fill_labels = c("0", "2", "4", "\u2265 6"),
                                                  land_sf = world_land)

@@

ggsave(paste0(results_dir, "subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 12.5)

@@

```{r}
# Median
median_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "med_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,6, by = 2),
                                                  fill_limits = c(0,6),
                                                  fill_labels = c("0", "2", "4", "\u2265 6"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

# Mean
mean_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,6, by = 2),
                                                  fill_limits = c(0,6),
                                                  fill_labels = c("0", "2", "4", "\u2265 6"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

# Weighted Mean
w_mean_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
                                                  res = "region",
                                                  fill = "w_mean_BC_subs_KWh",
                                                  fill_name = "Subsidy Intensity \n($/KWh)",
                                                  fill_breaks = seq(0,6, by = 2),
                                                  fill_limits = c(0,6),
                                                  fill_labels = c("0", "2", "4", "\u2265 6"),
                                                  land_sf = world_land,
                                                  region_sf = fao_regions)

@@

ggsave(paste0(results_dir, "subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 12.5)

@@

```{r, fig.width=14, fig.height=12.5}
# Combine into six panel
subsidy_intensity_BC_noleg <- plot_grid(median_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
                                       median_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
                                       mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
                                       mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
                                       w_mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
                                       w_mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
                                       ncol = 2,
                                       labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean", ""),
                                       label_x = c(-0.04, 0, -0.03,0, -0.1, 0))

subsidy_intensity_BC_map <- plot_grid(subsidy_intensity_BC_noleg,
                                       intensity_BC_region_legend,
                                       rel_heights = c(2,0.2),
                                       ncol = 1)

subsidy_intensity_BC_map

ggsave(paste0(results_dir, "subsidy_intensity_BC_map.png"), dpi = 200, width = 14, height = 12.5)
```

@@

```{r}
# Median
median_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
                                     res = "region",
                                     fill = "med_f_v_fmsy",
                                     fill_name = "F/Fmsy",
                                     fill_breaks = seq(0,4, by = 1),
                                     fill_limits = c(0,4),
                                     fill_labels = c("0", "1", "2", "3", "\u2265 4"),
                                     land_sf = world_land,
                                     region_sf = fao_regions)

@@

# Mean
mean_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
                                     res = "region",
                                     fill = "mean_f_v_fmsy",
                                     fill_name = "F/Fmsy",
                                     fill_breaks = seq(0,4, by = 1),
                                     fill_limits = c(0,4),
                                     fill_labels = c("0", "1", "2", "3", "\u2265 4"),
                                     land_sf = world_land,
                                     region_sf = fao_regions)

@@

# Weighted Mean
w_mean_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
                                     res = "region",
                                     fill = "w_mean_f_v_fmsy",
                                     fill_name = "F/Fmsy",
                                     fill_breaks = seq(0,4, by = 1),
                                     fill_limits = c(0,4),
                                     fill_labels = c("0", "1", "2", "3", "\u2265 4"),
                                     land_sf = world_land,
                                     region_sf = fao_regions)

@@

### B/Bmsy by Region

```{r}
# Median
median_b_v_bmsy_region_map <- MapMaker(data = upsides_region, 
                                     res = "region",
                                     fill = "med_b_v_bmsy",
                                     fill_name = "B/Bmsy",
                                     fill_breaks = seq(0,2, by = 0.5),
                                     fill_limits = c(0,2),
                                     fill_labels = c("0", "0.5", "1", "1.5", "\u2265 2"),
                                     land_sf = world_land,
                                     region_sf = fao_regions)

ggsave(paste0(results_dir, "median_b_v_bmsy_region_map.png"), dpi = 200, width = 7, height = 5)

# Mean
mean_b_v_bmsy_region_map <- MapMaker(data = upsides_region, 
                                     res = "region",
                                     fill = "mean_b_v_bmsy",
                                     fill_name = "B/Bmsy",
                                     fill_breaks = seq(0,2, by = 0.5),
                                     fill_limits = c(0,2),
                                     fill_labels = c("0", "0.5", "1", "1.5", "\u2265 2"),
                                     land_sf = world_land,
                                     region_sf = fao_regions)

ggsave(paste0(results_dir, "mean_b_v_bmsy_region_map.png"), dpi = 200, width = 7, height = 5)

# Weighted Mean
w_mean_b_v_bmsy_region_map <- MapMaker(data = upsides_region, 
                                     res = "region",
                                     fill = "w_mean_b_v_bmsy",
                                     fill_name = "B/Bmsy",
                                     fill_breaks = seq(0,2, by = 0.5),
                                     fill_limits = c(0,2),
                                     fill_labels = c("0", "0.5", "1", "1.5", "\u2265 2"),
                                     land_sf = world_land,
                                     region_sf = fao_regions)

ggsave(paste0(results_dir, "w_mean_b_v_bmsy_region_map.png"), dpi = 200, width = 7, height = 5)

# Combine into three panel
b_v_bmsy_region_legend <- get_legend(w_mean_b_v_bmsy_region_map)

b_v_bmsy_region_map <- plot_grid(median_b_v_bmsy_region_map + theme(legend.position = "none"),
                                 mean_b_v_bmsy_region_map + theme(legend.position = "none"),
                                 w_mean_b_v_bmsy_region_map + theme(legend.position = "none"),
                                 b_v_bmsy_region_legend,
                                 ncol = 1,
                                 rel_heights = c(1, 1, 1, 0.2),
                                 labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
                                 label_x = c(-0.04, -0.03, -0.1, 0),
                                 align = "v")

b_v_bmsy_region_map
ggsave(paste0(results_dir, "b_v_bmsy_region_map.png"), dpi = 200, width = 7, height = 12.5)
```

@@

```{r}
subsidy_intensity_upsides_region <- upsides_region %>%
  left_join(subsidy_intensity_region, by = "fao_region")
```

```{r}
# Set some plot scales
subs_x <- c(0,2.5)
f_y <- c(0,3)
effort_fill_lim <- c(0,7.5e9)
effort_fill_breaks <- seq(0,7.5e9, length.out = 5)
effort_fill_labels <- format(seq(0,7.5e9, length.out = 5)/1e9, scientific = F, digits = 2)

# Labels
w_mean_subs_label <- "Weighted Mean Subsidy Intensity ($/KWh)"
mean_subs_label <- "Mean Subsidy Intensity ($/KWh)"
median_subs_label <- "Median Subsidy Intensity ($/KWh)"

w_mean_f_label <- "Weighted Mean F/Fmsy"
mean_f_label <- "Mean F/Fmsy"
median_f_label <- "Median F/Fmsy"

effort_label <- "Total Fishing Effort \n(KWh, billions)"
```

### Use Weighted Mean Subsidies

#### Total Subsidies

```{r}
# Weighted Mean Total Subs vs Median F/Fmsy [LAST]
w_mean_tot_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
                                       res = "corr",
                                       x = "w_mean_tot_subs_KWh",
                                       x_name = w_mean_subs_label,
                                       x_limits = subs_x,
                                       y = "med_f_v_fmsy",
                                       y_name = median_f_label,
                                       y_limits = f_y,
                                       fill = "tot_fishing_KWh",
                                       fill_name = effort_label,
                                       fill_limits = effort_fill_lim,
                                       fill_breaks = effort_fill_breaks,
                                       fill_labels = effort_fill_labels)

# Weighted Mean Total Subs vs Mean F/Fmsy [BEST]
w_mean_tot_vs_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
                                       res = "corr",
                                       x = "w_mean_tot_subs_KWh",
                                       x_name = w_mean_subs_label,
                                       x_limits = subs_x,
                                       y = "mean_f_v_fmsy",
                                       y_name = mean_f_label,
                                       y_limits = f_y,
                                       fill = "tot_fishing_KWh",
                                       fill_name = effort_label,
                                       fill_limits = effort_fill_lim,
                                       fill_breaks = effort_fill_breaks,
                                       fill_labels = effort_fill_labels)

# Weighted Mean Total Subs vs Weighted Mean F/Fmsy [SECOND]
w_mean_tot_vs_w_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
                                       res = "corr",
                                       x = "w_mean_tot_subs_KWh",
                                       x_name = w_mean_subs_label,
                                       x_limits = subs_x,
                                       y = "w_mean_f_v_fmsy",
                                       y_name = w_mean_f_label,
                                       y_limits = f_y,
                                       fill = "tot_fishing_KWh",
                                       fill_name = effort_label,
                                       fill_limits = effort_fill_lim,
                                       fill_breaks = effort_fill_breaks,
                                       fill_labels = effort_fill_labels)

# Combine into three panel
corr_legend <- get_legend(w_mean_tot_vs_w_mean_f_v_fmsy_plot)

w_mean_tot_vs_f_v_fmsy_plot <- plot_grid(

  plot_grid(w_mean_tot_vs_median_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
            w_mean_tot_vs_mean_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
            w_mean_tot_vs_w_mean_f_v_fmsy_plot + theme(legend.position = "none"),
            ncol = 1,
            align = "hv"),
  corr_legend,
  ncol = 1,
  rel_heights = c(3, 0.2))

w_mean_tot_vs_f_v_fmsy_plot
ggsave(paste0(results_dir, "w_mean_tot_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 12.5)
```

#### Bad Subsidies
